Reliable error estimation for Sobol' indices

### 2016-08-09 article.tex
changes L, sections 4.1 4.2

\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
\begin{align*}
S_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
\end{align*}
Therefore, we can define $S_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$. If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
\begin{align*}
\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
\end{align*}
where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.

@@

The recursive estimation procedure we propose combine the error bound presented in the previous section with one of the two estimation strategies of section \ref{estimation.strategies}. Namely, Saltelli's strategy and the one based on replicated designs. The form of the error bound is the same for both strategies and is given by equation \ref{}.

We start be detailing our recursive procedure in the form of an algorithm. Then, we discuss a possible improvement by considering an estimator recently introduced by Owen improving the estimation of small first-order indices.

\subsection{Main algorithm}
%
%$\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can either be used with procedure $A$ to estimate all first-order and all total effect Sobol' indices or with procedure $B$ to estimate all first-order Sobol' indices. Algorithms \ref{procedureA} and \ref{procedureB} summarize the main steps of each procedure.
%\begin{algorithm}[!ht]
%\caption{Procedure $A$}
%\begin{algorithmic}[1]
%\vspace*{0.2cm}
%\State Set: $\ell \leftarrow 1$, $\mathcal{P}_{0} \leftarrow B_0$, ${\mathcal{P}'}_{0} \leftarrow {B'}_0$
%\While {stopping criterion}
%\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
%
%\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
%\State Compute $\{f(\vx_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$
%\For {$u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$}
%\State Construct design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i=2^{\ell-1}}^{2^{\ell}-1}$
%\State Compute  $\{f(\vx_{i,u},{\vx'}_{i,-u})\}_{i=2^{\ell-1}}^{2^\ell-1}$
%\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ with formula (\ref{first.order.est.rec}) and (\ref{total.effect.est.rec})
%\EndFor
%\State $\ell \leftarrow \ell + 1$
%\EndWhile
%\State Return $\widehat{\underline{\tau}_u^2}^{(\ell)}$ and $\widehat{\ov{$\tau$}_u^2}^{(\ell)}$ for all $u \in \mathcal{D}$.
%\end{algorithmic}
%\label{procedureA}
%\end{algorithm}
%\begin{algorithm}[!ht]
%\caption{Procedure $B$}
%\begin{algorithmic}[1]
%\vspace*{0.2cm}
%\State Set: $\ell \leftarrow 1$, $\mathcal{P}_{0} \leftarrow B_0$, ${\mathcal{P}'}_{0} \leftarrow {B'}_0$
%\While {stopping criterion}
%\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$
%
%\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
%\State Compute $\{f(\vx_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ and $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$
%\For {$u \in \mathcal{D}$}
%\State  order $\{f({\vx'}_i)\}_{i=2^{\ell-1}}^{2^\ell-1}$ into $\{\pi_u(f({\vx'}_i))\}_{i=2^{\ell-1}}^{2^\ell-1}$
%\State Estimate $\widehat{\underline{\tau}_u^2}^{(\ell)}$ with formula (\ref{first.order.est.rec})
%\EndFor
%\State $\ell \leftarrow \ell + 1$
%\EndWhile
%\State Return $\widehat{\underline{\tau}_u^2}^{(\ell)}$ for all $u \in \mathcal{D}$.
%\end{algorithmic}
%\label{procedureB}
%\end{algorithm}
%
\subsection{Improvements}

We focus on the use of a better estimator to evaluate small first-order Sobol' indices in Variant $A$. This estimator is called ``Correlation 2" and was introduced by Owen in \cite{Owen}. Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small closed Sobol' indices. Our aim is to show that using ``Correlation 2" in procedure $A$ may reduce the total number of model evaluations. Its formula writes as follows:
\begin{equation}
\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)),
\label{correlation2}
\end{equation}
It uses an extra set of $n$ model evaluations to estimate $\widehat{\underline{\tau}_u^2}$. %Owen explains the effectiveness of (\ref{correlation2}) as follows. If the main effect of $\vx_u$ is small then $f(\vx)$ will be almost entirely explained by $\vx_{-u}$. The two terms $(f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))$ and $(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i))$ should then be small quantities as well as (\ref{correlation2}). 
\bigskip

We discuss now the potential improvement brought by the use of ``Correlation 2" in Variant $A$. The idea is to replace the current estimator (\ref{first.order.est}) by (\ref{correlation2}) for each small first-order index. Assume that the number of small first-order indices is known and equals $\gamma$. We denote by $u_1,\dots,u_{\gamma}$ the indexes of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$. The cost of Variant $A$ including ``Correlation 2" writes: 
\begin{equation}
2 \sum \limits_{j \in \Gamma} n'_{u_j} + \sum \limits_{j \in \mathcal{D}/\Gamma} n'_{u_j} + 2 \ n'_{\max},
\label{cost.improvement}
\end{equation}
where: \begin{itemize}
\item[$\bullet$] $2 \sum \limits_{j \in \Gamma} n'_{u_j}$ is the number of evaluations induces by the $\gamma$ sets \\ $\{f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)\}_{i=0}^{n'_{u_j}-1}$ and $\gamma$ sets $\{f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)\}_{i=0}^{n'_{u_j}-1}$,
\item[$\bullet$] $\sum \limits_{j \in \mathcal{D}/\Gamma} n'_{u_j}$ is the number of evaluations induced by the $d-\gamma$ sets \\ $\{f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)\}_{i=0}^{n'_{u_j}-1}$, 
\item[$\bullet$] $2 \ n'_{\max}=2 \ \max \limits_{j \in \mathcal{D}} \ (n'_{u_j})$, is the number of evaluations induced by the $2$ sets $\{f\left(\vx_{i}\right)\}_{i=0}^{n'_{\max}-1}$ and $\{f\left({\vx'}_{i}\right)\}_{i=0}^{n'_{\max}-1}$.
\end{itemize}
At the opposite, the cost of Variant $A$ excluding ``Correlation 2" writes: 
\begin{equation}
\sum \limits_{j \in \mathcal{D}} n_{u_j} + 2 \ n_{\max}.
\label{cost.non.improvement}
\end{equation}
The comparison between (\ref{cost.improvement}) and (\ref{cost.non.improvement}) is driven by whether or not total effect indices require more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than their respective first-order indices. We distinguish two extreme cases :
\begin{itemize}
\item[1)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$. As a result, the difference (\ref{cost.improvement}) - (\ref{cost.non.improvement}) is always positive. Thus, using ``Correlation 2" results in a cost regression.
\item[2)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires less evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$. As a result, the difference (\ref{cost.improvement}) - (\ref{cost.non.improvement}) is always negative. Thus, using ``Correlation 2" results in a cost improvement.
\end{itemize}
The standard case varies between these two. That is a portion of indices $\ov{$S$}_j$ require more evaluations and another portion of $\ov{$S$}_j$ require less. Illustrations of this potential improvement are addressed in Section \ref{appli}. 
\bigskip

In pratice, one does not know which are the small Sobol' indices. To overcome this issue, we proceed as follows in Variant $A$:
... etc ...

%The second improvement focus on the choice of the $2d$ generating matrices that generate the two Sobol' sequences $\mathcal{P}_\ell$  and ${\mathcal{P}'}_\ell$ in procedure $B$.
%
%We note by $C_1,\dots,C_d$ the matrices generating $\mathcal{P}_\ell=\{\vx_i\}_{i=0}^{2^\ell-1}$ and ${C'}_1,\dots,{C'}_d$ those generating $\mathcal{P}'_\ell=\{{\vx'}_i\}_{i=0}^{2^\ell-1}$.
%In the multiplicative approach \cite{crass}, these $2d$ matrices are selected as the first $2d$ elements of the set found by Kuo and Joe in \cite{Kuo}. This set is composed of generating matrices that optimize the $2$-dimensional projection $t$-values. 
%
%%In procedure $A$, each design $\{\vx_{i,u},{\vx'}_{i,-u}\}_{i\geq0}$ constructed in step $6$ of Algorithm \ref{procedureA} is a $d$-dimensional Sobol' sequence generated by the $d$-subset: $${C'}_1,\dots,{C'}_{u-1},C_u,{C'}_{u+1},\dots,C_d.$$ Therefore, $2$-dimensional projection $t$-values are still optimized.
%
%In procedure $B$, each permutation $\pi_u$ applied in step $6$ of Algorithm \ref{procedureB} results in a design $\{\vx_{i,u}:{\vx'}_{\pi_u(i),-u}\}_{i=0}^{2^\ell-1}$. The $d$ generating matrices corresponding to this design are:
%$${C'}_1U_u,\dots,{C'}_{u-1}U_u,C_u,{C'}_{u+1}U_u,{C'}_dU_u$$ where $U_u$ is a a full rank upper triangular matrix verifying $C_u={C'}_uU_u$. The right multiplication by $U_u$ is the digital representation of the ordering by $\pi_u$.

%\section{Estimators: Correlation 2 Oracle 2}
%\subsection{Choice and parameters (threshold small?)}
%\subsection{Cost discussion: for first-order Consider or not total order}

>>>>

\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
\begin{align*}
\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
\end{align*}
Therefore, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$. If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
\begin{align*}
\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
\end{align*}
where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.

@@

The recursive estimation procedure we propose combine the error bound presented in the previous section with one of the two estimation strategies of section \ref{estimation.strategies}. Namely, Saltelli's strategy and the one based on replicated designs. The form of the stopping criterion is the same for both strategies. It is defined as $\abs{\varepsilon_{S_u}} \leq \epsilon$, where $\epsilon$ is the desired precision on the Sobol' indices.

We start be detailing our recursive procedure in the form of an algorithm. Then, we discuss a possible improvement by considering a new estimator recently introduced in \cite{Owen} for first-order indices.

\subsection{Recursive procedure algorithm}

Algorithm \ref{recursive.algorithm} summarizes the main steps of our recursive procedure. First, choose the target tolerance $\epsilon >0$. Choose $r \in \mathbb{N}$ large enough to satisfy the cone conditions (\ref{}) and balance the inflation factor $a(r,\ell)$. Set $\ell=r-1$ and construct the two starting designs $\mathcal{P}_{\ell}=\{\vx_i\}_{i=0}^{2^\ell-1}$ and $\mathcal{P}'_{\ell}=\{\vx'_i\}_{i=0}^{2^\ell-1}$ accordingly to the multiplicative approach detailed in \cite{crass}.

With this construction, at each step $\ell$, $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ correspond to the first $2^\ell$ points of two Sobol' sequences. Furthermore, they possess the structure of two replicated designs of order $1$.
\bigskip

Then, $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can either be used with Saltelli's strategy to estimate all first-order indices and total effect Sobol' indices. This option is referred as Variant $A$ in Algorithm \ref{recursive.algorithm}. Or $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$ can be used with the replication procedure to estimate all first-order Sobol' indices. This option is referred as Variant $B$ in Algorithm \ref{recursive.algorithm}.

If the stopping criterion is satisfied, the algorithm stops and Sobol' estimates are returned. Otherwise, $\ell$ is incremented by one and a new set of $2^{\ell}$ points is added to each design $\mathcal{P}_{\ell}$ and $\mathcal{P}'_{\ell}$.

\begin{algorithm}[!ht]
\caption{Recursive estimation of Sobol' indices}
\begin{algorithmic}[1]
\vspace*{0.2cm}
\State Choose $\epsilon >0$ and $r \in \mathbb{N}$
\State Set: $\ell \leftarrow r-1$, 
\While {$\abs{\varepsilon_{S_u}} \leq \epsilon$}
\State $\mathcal{P}_\ell \leftarrow \mathcal{P}_{\ell-1} \cup B_\ell$

\hspace*{-0.3cm} $\mathcal{P}'_\ell \leftarrow \mathcal{P}'_{\ell-1} \cup {B'}_\ell$
\For {$u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$}
\If {Variant $A$}
\State Estimate $\widehat{\underline{S}_u}^{(\ell)}$ and $\widehat{\ov{$S$}_u}^{(\ell)}$ with formula \ref{} and Saltelli's strategy
\EndIf
\If {Variant $B$}
\State Estimate $\widehat{\underline{S}_u}^{(\ell)}$ with formula \ref{} and the replication procedure
\EndIf
\EndFor
\State $\ell \leftarrow \ell + 1$
\EndWhile
\State Return the Sobol' estimates.
\end{algorithmic}
\label{recursive.algorithm}
\end{algorithm}

The cost of our algorithm varies whether Variant $A$ or Variant $B$ is selected. To discuss this cost we note by $\ell^\star$ the ending iteration. If Variant $A$ is selected the cost of our algorithm writes:
\begin{equation*}
\sum \limits_{j \in \mathcal{D}} 2^{\ell_j} + 2 \times 2^{\ell^{\star}},
\end{equation*}
where: 
\begin{itemize}
\item[$\bullet$] $2^{\ell_j}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ used to estimate both $\underline{S}_j$ and $\overline{S}_j$.
\item[$\bullet$] $2 \times 2^{\ell^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
\end{itemize}
This cost can be seen as a generalisation of the one specified in Theorem \ref{saltelli.theorem}. If all $\ell_j$ are equal, the cost of Variant $A$ becomes $2^{\ell^\star}(d+2)$ and we recover the cost of Theorem \ref{saltelli.theorem} with $n=2^{\ell^\star}$.

If Variant $B$ is selected the cost of our algorithm equals $2 \times 2^{\ell^{\star}}$. This cost corresponds to the one specified in the replication procedure with $n=2^{\ell^{\star}}$.

\subsection{Improvements}

We focus on the use of a better estimator to evaluate small first-order Sobol' indices in Variant $A$. This estimator is called ``Correlation 2" and was introduced by Owen in \cite{Owen}. Owen discussed and highlighted the efficiency of ``Correlation 2" when estimating small closed Sobol' indices. Our aim is to show that using ``Correlation 2" in procedure $A$ may reduce the total number of model evaluations. Its formula writes as follows:
\begin{equation}
\widehat{\underline{\tau}_u^2} = \frac{1}{n} \sum \limits_{i=0}^{n-1} (f(\vx_i)-f({\vz}_{i,u}:{\vx}_{i,-u}))(f(\vx_{i,u}:{\vx'}_{i,-u})-f({\vx'}_i)),
\label{correlation2}
\end{equation}
where $(\vx_i,{\vx'}_i, \vz_i) \iid [0,1)^{3d}$. It uses an extra set of $n$ model evaluations to estimate $\underline{\tau}_u^2$.
\bigskip

We discuss now the potential improvement brought by the use of ``Correlation 2" in Variant $A$. The idea is to replace the current estimator (\ref{first.order.est}) by (\ref{correlation2}) for each small first-order index. Assume that the number of small first-order indices is known and equals $\gamma$. We denote by $u_1,\dots,u_{\gamma}$ the indexes of the corresponding inputs and $\Gamma = \{1,\dots,\gamma\}$. The cost of Variant $A$ including ``Correlation 2" rewrites: 
\begin{equation}
\sum \limits_{j \in \Gamma} 2 \times 2^{\ell'_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{\ell_{u_j}} + 2 \times 2^{\ell^\star}, \qquad \ell'_{u_j}\leq \ell^{\star}, \ \ell_{u_j} \leq \ell^{\star},
\label{cost.improvement}
\end{equation}
where: \begin{itemize}
\item[$\bullet$] for $j\in \Gamma$, $2 \times 2^{\ell'_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ and $f\left(\vz_{i,u_j}:\vx_{i,-u_j}\right)$ to estimate small first-order indices,
\item[$\bullet$] for $j\in \mathcal{D}/\Gamma$, $ 2^{\ell_{u_j}}$ is the number of evaluations $f\left(\vx_{i,j}:{\vx'}_{i,-j}\right)$ to estimate non small first-order indices,
\item[$\bullet$] $2 \times 2^{\ell^{\star}}$ is the number of evaluations $f\left(\vx_{i}\right)$ and $f\left({\vx'}_{i}\right)$ used in the estimation of each first-order and total effect index.
\end{itemize}
At the opposite the cost of Variant $A$ without  ``Correlation 2" writes:
\begin{equation}
\sum \limits_{j \in \Gamma} 2^{\ell_{u_j}} + \sum \limits_{j \in \mathcal{D}/\Gamma} 2^{\ell_{u_j}} + 2 \times 2^{\ell^{\star}}, \qquad \ell_{u_j} \leq \ell^{\star}.
\label{cost.non.improvement}
\end{equation}

The difference between costs (\ref{cost.improvement}) and (\ref{cost.non.improvement}) equals:
\begin{equation}
 \sum \limits_{j \in \Gamma} 2^{\ell'_{u_j}+1} - 2^{\ell_{u_j}}.
\label{cost.comparison}
\end{equation}
Hence, the sign of this difference indicates whether or not using ``Correlation 2" bring an improvement to Variant $A$. We distinguish two extreme cases :
\begin{itemize}
\item[1)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires as much or more evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$. As a result, the difference (\ref{cost.comparison}) is always positive and using ``Correlation 2" leads to a cost regression.
\item[2)] $\forall j \in \Gamma$, the total effect index $\ov{$S$}_j$ requires less evaluations $f\left(\vx_{i,u_j}:{\vx'}_{i,-u_j}\right)$ than the first-order index $\underline{S}_j$. As a result, the difference (\ref{cost.comparison}) is always negative or null and using ``Correlation 2" may provide a cost improvement.
\end{itemize}
Other cases vary between these two. That is, some indices $\ov{$S$}_j$ require more evaluations than $\underline{S}_j$ and others require less. Illustrations of this potential improvement are addressed in Section \ref{appli}. 
\bigskip

In pratice, one does not know which are the small Sobol' indices. To overcome this issue, we propose the following alternative for Variant $A$. Assume that there exists one or multiple  $u \in \mathcal{D}$ such that estimates $\widehat{\underline{S}_u}^{(\ell)}$ are smaller than a specified threshold at the end of the first iteration. Then, for these indices, at the next iteration estimator (\ref{first.order.est}) is switched for (\ref{correlation2}) and a third Sobol' sequence $\mathcal{P''}_{\ell}=\{\vz_i\}_{i=0}^{2^\ell-1}$ is constructed for the evaluations $f({\vz}_{i,u}:{\vx}_{i,-u})$.
